\section{Notes on using trace results}

 {\bf Coverage.} The trace  results are commonly expressed in terms of coverage: the residue is
important if its ``coverage'' is small - that is if it belongs to some small top percentage of residues [100\% is
 all of the residues in a chain], according to trace.
The ET results are presented  in form of a table, usually with a small number of 
clustering residues, sorted by the strength of the evolutionary pressure(as we infer it).
(The smaller the coverage, the stronger the pressure on the residue.) Starting from the top of that list,
mutating a couple of residues should affect the protein somehow -  how exactly, we should hopefully learn from
the experiment.

 {\bf Known substitutions.} One of the table columns is ``substitutions''
- other amino acid types seen at the same position in the alignment. These amino acid types may be interchangeable
at that position in the protein, so if one wants to affect the protein by a point mutation, they should be avoided.
For example if the substitutions are ``RVK'' and my original protein has an R at that position, it is advisable to
try anything, but RVK. To the contrary, if I am looking for substitutions which will {\emph not}  affect the protein,
I may try replacing, R with K, or more surprisingly, with V. The percentage of times the substitution appears in the
alignment if given in the immediately following bracket. No percentage is given in the cases when it is smaller than 1.
This is meant ot be a rough guide - due to rounding errors these percentages often do not add up to 100.

{\bf Surface.} Also, where it may be of interest a column ``surf'' (for surface) appears. It signals that the
residue is solvent accessible (according to DSSP program) by at least 10\AA$^2$, 
which is roughly the area  needed for one water molecule
to come in the contact with the residue. But note that, if our picture of protein evolution is
correct, the neighboring residues which {\emph do \emph not} stick out directly to the surface might be equally important
in maintaining the interaction specificity - they should not be automatically dropped from consideration when
choosing the set for mutagenesis. (Especially if they form  a cluster with the surface residues.)

{\bf Number of contacts.} Another column worth noting is denoted ``noc (bb)'' it tells the number of contacts heavy atoms
of the residue in question make across the interface, as well as  how many of them are realized through
the backbone atoms (if all or most contacts are through the backbone, mutation presumably won't have strong impact).
Two heavy atoms are considered to be ``in contact'' if their centers are closer than $5\AA$.

{\bf Annotation.} If the residue annotation is available (either from the pdb file or from other sources), another column,
with the header ``annotation'' appears. Annotation carried over from from PDB is the following: 
site (indicating existence of related  site record in PDB ), ss bond (disulfide bond forming residue),  
hbond (hydrogen bond forming residue, jbond (james bond forming residue), and salt bridge (for salt bridge
forming residue).

{\bf Mutation suggestions.} Mutation suggestions are completely heuristic and based on complementarity with the substitutions found
in the alignment. Note that they are meant to be {\bf disruptive}.
The attempt is made to complement the following properties: size (small $[AVGSTC]$, medium $[
LPNQDEMIK]$, large $[WFYHR]$), 
hydrophobicity (hydrophobic $[LPVAMWFI]$, polar $[GTCY]$), charge (positive $[KHR]$,
 negative $[DE]$), aromaticity $[WFYH]$, long aliphatic chain \\$[EKRQM]$, 
 OH-group possession $[SDETY]$, and NH2 group possession $[NQRK]$.
The suggestions are listed according to how different they appear from the original amino acid, 
and they are grouped in round bracket   
if they appear equally good (or rather,equally  destructive) as mutation for the original.

